---
title: "Assignment B1"
author: "Raveen Badyal"
date: "3-Nov-2023"
output: github_document
---

```{r}

library(tidyverse)
library(lubridate)
library(devtools)
library(testthat)
library(digest)
```

### Exercise 1-2: Make and Document a Function


```{r}
#' Title: Pounds to Kilograms
#'
#' My function will take an input, in pounds, and return the conversion to kilograms rounded to 1 decimal point for conciseness.
#'
#' @param The argument for this function is lb. The symbol/abbreviation for pounds in lb. This is a numeric argument.
#'
#' @return The function returns a number, kg, which is the converted inputted pounds into kilograms. The output is limited to two digits for conciseness.
```

```{r}
lb_to_kg <- function(lb) {
  if(!is.numeric(lb)) {
    return('This function only works for numeric input.')
  }
  if(lb < 0.02) {
    return("Your input for lb is too small for this function")
  }
  kg <- round(lb / 2.20462, digits = 2)
  return (kg)
}
```

### Exercise 3: Include examples

The following examples are a few numeric inputs for lb, including one input with decimal places. I have included a smaller number, and a larger number, also the same with decimals, an very small input less than 1 and an input with many decimal places. At first, I limited my function to two digits total. When I tested the below inputs with that function, the larger number inputs were capped, and returned "454". I was able to see an error in the functionality of my function, and changed the function so there was a limit on decimal places and not the number of digits of the output.
```{r}
lb_to_kg(0.0343)
lb_to_kg(5)
lb_to_kg(1)
lb_to_kg(10)
lb_to_kg(1000)
lb_to_kg(1000.474745)
```
The following examples are numeric inputs for lb, that are too small to acheive a result as this function's output is limited to 2 decimal points.
```{r}
lb_to_kg(0)
lb_to_kg(0.019)
lb_to_kg(0.002)
```

The following examples are non-numeric inputs for lb.
```{r}
lb_to_kg("Hi")
lb_to_kg(TRUE)
```
### Exercise 4: Test the Function
There is one test to determine if the function gives an error for inputs less than 0.02. The next test tests if there will be a valid output for 0.02 to test the bounds of the function. Finally, for numbers, there is a "normal" number to ensure the function will work on more usual inputs. The last test is for a non-numeric input, to see if we will get the correct error message.
```{r}
test_that("Testing lb to kg conversion function", {
  expect_equal(lb_to_kg(0), "Your input for lb is too small for this function")
  expect_equal(lb_to_kg(0.02), 0.01)
  expect_equal(lb_to_kg(10), 4.54)
  expect_equal(lb_to_kg("hi"), "This function only works for numeric input.")
})
```

